### 2010-09-04 Spatial_adaptation/standing-variation.tex
/* Standing variation */  adjustments and constant-speed beginning

Now let $f(t) = vt$, so $h(t) = \frac{ \omega_d v^d }{ d+1 } t^{d+1}$.
The integrals that appear above are of the following form, for $\alpha$, $\beta$, $a$, $b$, and $c$ all nonnegative:
\begin{align}
  \int_0^\infty t^c \exp \left( - \alpha t^a - \beta t^b \right) dt 
            &= \left( b^{-1} \beta^{ (1-c)/b } \right) \int_0^\infty u^{(c+1-b)/b} \exp\left( - \alpha \beta^{-a/b} u^{a/b} - u \right) du ,
\end{align}
so it suffices to learn something about the function
\begin{equation}
    G(a,b,x) := \int_0^\infty  t^a \exp\left( -x t^b - t \right) dt ,
\end{equation}
for $a$, $b$, and $x$ nonnegative.  We will only be interested in this as a function of $x$; 
the coefficients $a$ and $b$ will merely depend on the dimension and what quantity we are calculating.
We can construct a power series for $G$ in $x$:
\begin{align}
    \partial_x^n G(a,b,x) &= \int_0^\infty (-1)^n t^{a+nb} \exp\left( -x t^b - t \right) dt \\
            &= (-1)^n G(a+nb,b,x) , \quad \mbox{so} \\
    \partial_x^n G(a,b,x) \vert_{x=0} &= \Gamma(a+nb+1) .
\end{align}
So, if everything works out, we will have that
\begin{align}
    G(a,b,x) = \sum_{n \ge 0} \frac{(-x)^n}{n!} \Gamma(a+nb+1) .
\end{align}

@@

Now suppose that $b$ is rational (as will be the case), letting $b = b'/c$ with $b'$ and $c$ positive integers.
Therefore, setting $n = mc+\ell$,
\begin{align}
    G(a,b,x) &= \sum_{\ell=0}^{c-1} \sum_{m \ge 0} \frac{(-x)^{mc+\ell}}{(mc+\ell)!} \Gamma(a+\ell b'/c+mb'+1) \\
            &= \sum_{\ell=0}^{c-1} \sum_{m \ge 0} \frac{(-x)^{mc+\ell}}{(mc+\ell)!} (a+\ell b')_{mb'} \Gamma(a + \ell b') \\
            &= \sum_{\ell=0}^{c-1} \frac{ (-x)^{\ell} }{ \ell! } \sum_{m \ge 0} ( (-cx)^c / (b')^{b'} )^m 
                    \frac{ \prod_{j=0}^{b'-1} (\frac{ a+b'\ell+j }{ c b' } )_m }{ \prod_{k=0}^{c-1} (\frac{\ell+1+k}{c})_m } ,
\end{align}
which is the sum of $c$ (generalized) hypergeometric functions.

>>>>

Now let $f(t) = vt$, so $h(t) = \frac{ \omega_d v^d }{ d+1 } t^{d+1}$.
The integrals that appear above are of the following form:
\begin{align}
  \int_0^\infty t^c \exp \left( - \alpha t^a - \beta t^b \right) dt 
            &= \left( b^{-1} \beta^{ (1-c)/b } \right) \int_0^\infty u^{(c+1-b)/b} \exp\left( - \alpha \beta^{-a/b} u^{a/b} - u \right) du ,
\end{align}
so it suffices to learn something about the function
\begin{equation}
    G(a,b,x) := \int_0^\infty  t^a \exp\left( -x t^b - t \right) dt .
\end{equation}
We will only be interested in this as a function of $x$; 
the coefficients $a$ and $b$ will merely depend on the dimension and what quantity we are calculating.
We can construct a power series for $G$ in $x$:
\begin{align}
    \partial_x^n G(a,b,x) &= \int_0^\infty (-1)^n t^{a+nb} \exp\left( -x t^b - t \right) dt \\
            &= (-1)^n G(a+nb,b,x) , \quad \mbox{so} \\
    \partial_x^n G(a,b,x) \vert_{x=0} &= \Gamma(a+nb+1) .
\end{align}
So, if everything works out, we will have that
\begin{align}
    G(a,b,x) = \sum_{n \ge 0} \frac{(-x)^n}{n!} \Gamma(a+nb+1) .
\end{align}

@@

Now suppose that $b$ is rational (as will be the case), letting $b = b'/c$ with $b'$ and $c$ positive integers.
Therefore, setting $n = mc+\ell$,
\begin{align}
    G(a,b,x) &= \sum_{\ell=0}^{c-1} \sum_{m \ge 0} \frac{(-x)^{mc+\ell}}{(mc+\ell)!} \Gamma(a+\ell b'/c+mb'+1) \\
            &= \sum_{\ell=0}^{c-1} \sum_{m \ge 0} \frac{(-x)^{mc+\ell}}{(mc+\ell)!} (a+\ell b')_{mb'} \Gamma(a + \ell b') \\
            &= \sum_{\ell=0}^{c-1} \frac{ (-x)^{\ell} }{ \ell! } \Gamma(a + \ell b') \sum_{m \ge 0} ( (-cx)^c / (b')^{b'} )^m 
                    \frac{ \prod_{j=0}^{b'-1} (\frac{ a+b'\ell+j }{ b' } )_m }{ \prod_{k=0}^{c-1} (\frac{\ell+1+k}{c})_m } ,
\end{align}
which is the sum of $c$ (generalized) hypergeometric series.
For these to converge, we need $b' \le c$, e.g.\ $b\le 1$.

In particular, if we let $A=\lambda_0 \omega_d v^d $ and $B=\lambda h(1)$, then 
\begin{align}
    \E[\tau] &= \int_0^\infty e^{-A t^d - B t^{d+1} dt \\
            &= \frac{B^{1/(d+1)}}{d+1} \int_0^\infty u^{-d/(d+1))} \exp\left( -AB^{-d/(d+1))} u^{d/(d+1)} -u \right) du \\
            &= \frac{B^{1/(d+1)}}{d+1} G \left(-d/(d+1), d/(d+1), A B^{-d/(d+1)} \right) .
\end{align}
